---
title: "Presentation shinydashboard"
author: "DataKnowledge"
date: "October, 2015"
output:
  ioslides_presentation:
    css: css/shiny_niv1.css
    highlight: tango
    smaller: no
    transition: slower
    widescreen: yes
runtime: shiny
---

##  Shiny Dashboard

**shinydashboard** is an R package that allows to have a different organization of the application. 

A dashboard has three parts: 
  
- a header
- a sidebar
- a body

##  Shiny Dashboard
```{r, echo = FALSE, eval = TRUE}
rmarkdown::render_delayed({
  suppressPackageStartupMessages(library(shinydashboard))
  shinyApp(
    ui = dashboardPage(
      dashboardHeader(title = "Header"),
      dashboardSidebar("Sidebar"),
      dashboardBody("Body")
    ), 
    server = function(input, output) {}
  )
})
```

## Shiny Dashboard | The header | Properties

Change the color (among black, purple, green, red, and yellow):
```{r, echo = TRUE, eval = FALSE}
dashboardPage(skin = "red")
```

Add a title: 
```{r, echo = TRUE, eval = FALSE}
dashboardHeader(title = "My Dashboard")
```

Add some message menu:
```{r, echo = TRUE, eval = FALSE}
dropdownMenu(type = "messages",
             messageItem(from = "Sales Dept",
                         message = "Sales are steady this month."),
             messageItem(from = "New User", message = "How do I register?",
                         icon = icon("question"), time = "13:45"),
             messageItem(from = "Support", message = "The new server is ready.",
                         icon = icon("life-ring"), time = "2014-12-01")
)
```

## Shiny Dashboard | The header | Properties (2)

Add a notification menu:
  
```{r, echo = TRUE, eval = FALSE}
dropdownMenu(type = "notifications", badgeStatus = "success",
             notificationItem(text = "5 new users today", icon("users")),
             notificationItem(text = "12 items delivered", icon("truck"),
                              status = "success"),
             notificationItem(text = "Server load at 86%",
                              icon = icon("exclamation-triangle"),
                              status = "warning")
)
```

And a task menu:
  
```{r, echo = TRUE, eval = FALSE}
dropdownMenu(type = "tasks", badgeStatus = "success",
             taskItem(value = 90, color = "green", "Documentation"),
             taskItem(value = 17, color = "aqua", "Project X"),
             taskItem(value = 75, color = "yellow", "Server deployment"),
             taskItem(value = 80, color = "red", "Overall project")
)
```

## Shiny Dashboard: the header

```{r, echo = FALSE, eval = TRUE}
rmarkdown::render_delayed({
  suppressPackageStartupMessages(library(shinydashboard))
  shinyApp(
    ui = dashboardPage(
      skin = "red",
      dashboardHeader(title = "My Dashboard", 
                      dropdownMenu(type = "messages",
                                   messageItem(from = "Sales Dept", message = "Sales are steady this month."),
                                   messageItem(from = "New User", message = "How do I register?",
                                               icon = icon("question"), time = "13:45"),
                                   messageItem(from = "Support", message = "The new server is ready.",
                                               icon = icon("life-ring"), time = "2014-12-01")
                      ), 
                      dropdownMenu(type = "notifications", badgeStatus = "success",
                                   notificationItem(text = "5 new users today", icon("users")),
                                   notificationItem(text = "12 items delivered", icon("truck"),status = "success"),
                                   notificationItem(text = "Server load at 86%", icon = icon("exclamation-triangle"),
                                                    status = "warning")
                      ), 
                      dropdownMenu(type = "tasks", badgeStatus = "success",
                                   taskItem(value = 90, color = "green", "Documentation"),
                                   taskItem(value = 17, color = "aqua", "Project X"),
                                   taskItem(value = 75, color = "yellow", "Server deployment"),
                                   taskItem(value = 80, color = "red", "Overall project")
                      )
      ),
      dashboardSidebar("Sidebar"),
      dashboardBody("Body")
    ), 
    server = function(input, output) { }
  )
})
```

## Shiny Dashboard | The sidebar | Properties

The sidebar functions like a menu. It corresponds to the tabsetPanel of a regular shiny app, but horizontally. 
And each menu item corresponds to a tabPanel.

In the ui.R:
```{r, echo = TRUE, eval = FALSE}
dashboardSidebar(sidebarMenu(
  menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
  menuItem("Widgets", icon = icon("th"), tabName = "widgets")
)),
# Correspondance in the body:
dashboardBody(
  tabItems(
    tabItem(tabName = "dashboard", h2("Dashboard tab content")),
    tabItem(tabName = "widgets",h2("Widgets tab content"))
  )
)
```

## Shiny Dashboard | The sidebar | Properties (2)

You can also integrate any kind of input, just like in a regular shiny sidebar. But there is a specific input: a sidebarSearchForm, which is on top in the screenshot above.

This is essentially a specially formatted text input and and actionButton which appears as a icon (the icon can be changed with the icon argument): 
  
```{r, echo = TRUE, eval = FALSE}
sidebarSearchForm(textId = "searchText", buttonId = "searchButton",
                  label = "Search...")
```

## Shiny Dashboard: the sidebar

```{r, echo = FALSE, eval = TRUE}
rmarkdown::render_delayed({
  suppressPackageStartupMessages(library(shinydashboard))
  shinyApp(
    ui = dashboardPage(
      skin = "red",
      dashboardHeader(title = "My Dashboard", 
                      dropdownMenu(type = "messages",
                                   messageItem(from = "Sales Dept",
                                               message = "Sales are steady this month."),
                                   messageItem(from = "New User",
                                               message = "How do I register?",
                                               icon = icon("question"), time = "13:45"),
                                   messageItem(from = "Support",
                                               message = "The new server is ready.",
                                               icon = icon("life-ring"), time = "2014-12-01")
                      ), 
                      dropdownMenu(type = "notifications", badgeStatus = "success",
                                   notificationItem(text = "5 new users today",
                                                    icon("users")),
                                   notificationItem(text = "12 items delivered",
                                                    icon("truck"), status = "success"),
                                   notificationItem(text = "Server load at 86%",
                                                    icon = icon("exclamation-triangle"),
                                                    status = "warning")
                      ), 
                      dropdownMenu(type = "tasks", badgeStatus = "success",
                                   taskItem(value = 90, color = "green", "Documentation"),
                                   taskItem(value = 17, color = "aqua", "Project X"),
                                   taskItem(value = 75, color = "yellow",
                                            "Server deployment"),
                                   taskItem(value = 80, color = "red", "Overall project")
                      )
      ),
      dashboardSidebar(sidebarMenu(
        sidebarSearchForm(textId = "searchText", buttonId = "searchButton",
                          label = "Search..."),
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        menuItem("Widgets", icon = icon("th"), tabName = "widgets")
      )
      ),
      dashboardBody(tabItems(
        tabItem(tabName = "dashboard", h2("Dashboard tab content")),
        tabItem(tabName = "widgets",h2("Widgets tab content"))
      ))
    ), 
    server = function(input, output) { }
  )
})
```

## Shiny Dashboard | The Body | Properties

The body of a dashboard page can contain any regular Shiny content.

However, if you’re creating a dashboard you’ll likely want to make something that’s more structured. The basic building block of most dashboards is a box. 

- A basic box with an output:
```{r, echo = TRUE, eval = FALSE}
box(plotOutput("plot1"))
```

- A basic box with a title and some inputs:
```{r, echo = TRUE, eval = FALSE}
box(title = "Basic box - Inputs", background = "maroon", 
    sliderInput("slider", "Slider input:", 1, 100, 50),
    textInput("text", "Text input:")
)
```

## Shiny Dashboard | The Body | Properties (2)

- A box with a tabset panel:
```{r, echo = TRUE, eval = FALSE}
tabBox(title = "tabBox", id = "tabset1", height = "250px",
       tabPanel("Tab1", "First tab content"),
       tabPanel("Tab2", "Tab content 2")
)
```

- An info box:
```{r, echo = TRUE, eval = FALSE}
infoBox("Info box", 10 * 2, icon = icon("credit-card"))
```

- A value box:
```{r, echo = TRUE, eval = FALSE}
valueBox(10 * 2, "New Orders - value box", icon = icon("credit-card"))
```

## Shiny Dashboard: the body

```{r, echo = FALSE, eval = TRUE}
rmarkdown::render_delayed({
  suppressPackageStartupMessages(library(shiny))
  suppressPackageStartupMessages(library(shinydashboard))
  shinyApp(
    ui = dashboardPage(
      skin = "red",
      dashboardHeader(title = "My Dashboard", 
                      dropdownMenu(type = "messages",
                                   messageItem(from = "Sales Dept",
                                               message = "Sales are steady this month."),
                                   messageItem(from = "New User",
                                               message = "How do I register?",
                                               icon = icon("question"), time = "13:45"),
                                   messageItem(from = "Support",
                                               message = "The new server is ready.",
                                               icon = icon("life-ring"),
                                               time = "2014-12-01")
                      ), 
                      dropdownMenu(type = "notifications", badgeStatus = "success",
                                   notificationItem(text = "5 new users today",
                                                    icon("users")),
                                   notificationItem(text = "12 items delivered",
                                                    icon("truck"), status = "success"),
                                   notificationItem(text = "Server load at 86%",
                                                    icon = icon("exclamation-triangle"),
                                                    status = "warning")
                      ), 
                      dropdownMenu(type = "tasks", badgeStatus = "success",
                                   taskItem(value = 90, color = "green", "Documentation"),
                                   taskItem(value = 17, color = "aqua", "Project X"),
                                   taskItem(value = 75, color = "yellow",
                                            "Server deployment"),
                                   taskItem(value = 80, color = "red", "Overall project")
                      )
      ),
      dashboardSidebar(sidebarMenu(
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        menuItem("Widgets", icon = icon("th"), tabName = "widgets")
      )),
      dashboardBody(tabItems(
        tabItem(tabName = "dashboard", 
                h2("Dashboard tab content"), 
                fluidRow(box(plotOutput(outputId = "barChart")),
                         box(title = "Basic box - Inputs", background = "maroon", 
                             sliderInput("slider", "Slider input:", 1, 100, 50),
                             textInput("text", "Text input:")
                         )),
                fluidRow(tabBox(title = "tabBox", id = "tabset1", height = "250px",
                                tabPanel("Tab1", "First tab content"),
                                tabPanel("Tab2", "Tab content 2")),
                infoBox("Info box", 10 * 2, icon = icon("credit-card")),
                valueBox(10 * 2, "New Orders - value box", icon = icon("credit-card"))
                )
        ),
        tabItem(tabName = "widgets", h2("Widgets tab content"))
      ))
    ), 
    server = function(input, output) {
      output$barChart <- renderPlot(
        barplot(table(stats::rpois(100, lambda = 5)), col = rainbow(20))
      )
    }
  )
})
```